From massive collection of geo-located Tweets to a new geographical data source: Generating Twitter user mobility data from massive collection of geo-located Tweets

### 2016-02-29 Geo-located_Twitter_Data/latex/Geo_located_tweets.tex
new edits

\begin{document}
%\title{A new geographical data source: geo-located Twitter data}
%\title{A scalable geographical data framework for geo-located Twitter data}
%\title{From massive collection of geo-located Tweets to a new geographical data source}
\title{Generating Twitter user mobility data from massive collection of geo-located Tweets}

@@

\section*{Data collection}
In general, Twitter (http://www.twitter.com) offers two kinds of search API

>>>>

\begin{document}
%\title{A new geographical data source: geo-located Twitter data}
%\title{A scalable geographical data framework for geo-located Twitter data}
%\title{From massive collection of geo-located Tweets to a new geographical data source}
%\title{Generating Twitter user mobility data from massive collection of geo-located Tweets}

\title{From massive collection of geo-located Tweets to a new geographical data source: Generating Twitter user mobility data from massive collection of geo-located Tweets}

@@

Although Twitter data is accessible from its dedicated APIs, the collected data cannot be shared among
Furthermore, as the data is collected in a continuous fashion, the accumulated data

In this regard, this paper provides a scalable computing framework for efficient data processing.
In particular, this framework utilizes

\section*{Data collection}
In general, Twitter ({\tt{http://www.twitter.com}}) offers two kinds of search API
